Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-12-02 xrb2/paper.tex
Added info to acceleration table caption

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each simulation. $s_0$ is the speed at $t = 0$.}
	\tablehead{\colhead{run} & \colhead{$s_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)}} 
	\startdata
	{\tt F1000}     & $(3.41 \pm 0.01) \times 10^5$ & $(-1.03 \pm 0.13) \times 10^5$ \\
	{\tt F500}      & $(3.08 \pm 0.01) \times 10^5$ & $(5.41 \pm 0.19) \times 10^5$ \\
	{\tt F500\_2E8} & $(3.76 \pm 0.02) \times 10^5$ & $(1.74 \pm 0.17) \times 10^5$ \\
	{\tt F500\_3E8} & $(5.29 \pm 0.10) \times 10^5$ & $(3.57 \pm 0.02) \times 10^7$ \\
	\enddata
	%
\end{deluxetable}

Figure~\ref{fig:flame_speeds_1} gives position vs.\ time for the $\tt{F500}$ and $\tt{F1000}$ runs to show the dependence on rotation rate. As some of the hotter 500~Hz runs exhibit significant accelerations, we fit a quadratic curve to each set of data and calculate the acceleration and initial velocity from the fit parameters. These results are given in Table~\ref{table:flame_speeds}\MarginPar{How is the acceleration calculated for this table? I.e. Specifically, at what time / over what time window is it calculated?}.

@@

\begin{figure}[t]
	\centering
	\plotone{500Hz_stacked_enuc1_2order.pdf}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 0.02~\mathrm{s}$. Note that, due to its rapid acceleration, $\tt{F500\_3E8}$ (orange) is only run out to $\sim 70~\mathrm{ms}$ to avoid surpassing the domain boundary.}
\end{figure}

>>>>

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each simulation. $s_0$ is the speed at $t = 0$. The initial flame velocities and accelerations are derived from a quadratic least-squares fit to each of the datasets for times $t \gtrsim 0.02~\mathrm{s}$.}
	\tablehead{\colhead{run} & \colhead{$s_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)}} 
	\startdata
	{\tt F1000}     & $(3.41 \pm 0.01) \times 10^5$ & $(-1.03 \pm 0.13) \times 10^5$ \\
	{\tt F500}      & $(3.08 \pm 0.01) \times 10^5$ & $(5.41 \pm 0.19) \times 10^5$ \\
	{\tt F500\_2E8} & $(3.76 \pm 0.02) \times 10^5$ & $(1.74 \pm 0.17) \times 10^5$ \\
	{\tt F500\_3E8} & $(5.29 \pm 0.10) \times 10^5$ & $(3.57 \pm 0.02) \times 10^7$ \\
	\enddata
	%
\end{deluxetable}

Figure~\ref{fig:flame_speeds_1} gives position vs.\ time for the $\tt{F500}$ and $\tt{F1000}$ runs to show the dependence on rotation rate. As some of the hotter 500~Hz runs exhibit significant accelerations, we fit a quadratic curve to each set of data and calculate the acceleration and initial velocity from the fit parameters. These results are given in Table~\ref{table:flame_speeds}\MarginPar{How is the acceleration calculated for this table? I.e. Specifically, at what time / over what time window is it calculated?} \MarginPar{NF: I will update the error estimates}.

@@

\begin{figure}[t]
	\centering
	\plotone{500Hz_stacked_enuc1_2order.pdf}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 0.02~\mathrm{s}$. Note that, due to its rapid acceleration, $\tt{F500\_3E8}$ (orange) is only run out to $\sim 0.07~\mathrm{s}$ to avoid surpassing the domain boundary.}
\end{figure}
